Composite Bayesian inference in hindsight

### 2024-03-15 cv2/cv.tex
Update CV

\usepackage[T1]{fontenc}     % We are using pdfLaTeX,
\usepackage[utf8]{inputenc}  % hence this preparation
\usepackage[british]{babel}  
\usepackage[left = 0mm, right = 0mm, top = 0mm, bottom = 0mm]{geometry}
\usepackage[stretch = 25, shrink = 25]{microtype}  
\usepackage{graphicx}        % To insert pictures
\usepackage{xcolor}          % To add colour to the document
\usepackage{marvosym}        % Provides icons for the contact details

@@

\usepackage{FiraSans}        % Change this to use any font, but keep it simple
\renewcommand{\familydefault}{\sfdefault}

@@

% Centering without extra vertical spacing
\null\hfill
\begin{center}
\includegraphics[width=0.65\textwidth]{alexis_didimo_cropped.png}\\
\caption{\scriptsize My (hairless) digital twin}
\end{center}
\hfill\null

@@

\is
{\sc Research Assistant.} {\it University of Oxford}, UK. \dates{Apr 2001--Oct 2002} \\
\smaller{Developed advanced medical image registration algorithms and consulted for Mirada Solutions Ltd (now Siemens Molecular Imaging).}

>>>>

\usepackage[T1]{fontenc}     % We are using pdfLaTeX,
\usepackage[utf8]{inputenc}  % hence this preparation
\usepackage[british]{babel}  
\usepackage[left = 0mm, right = 0mm, top = 0mm, bottom = 0mm]{geometry}
%\usepackage[stretch = 25, shrink = 25]{microtype}  
\usepackage{graphicx}        % To insert pictures
\usepackage{xcolor}          % To add colour to the document
\usepackage{marvosym}        % Provides icons for the contact details

@@

\usepackage{FiraSans}        % Change this to use any font, but keep it simple
%\renewcommand{\familydefault}{\sfdefault}

@@

\null\hfill
\begin{center}
  \includegraphics[width=0.65\textwidth]{alexis_didimo_cropped.png}\\
  {\scriptsize My (hairless) digital twin.}
\end{center}
\hfill\null

@@

\is
{\sc Research Assistant.} {\it University of Oxford}, \hphantom{CACACACA} United Kingdom. \dates{Apr 2001--Oct 2002} \\
\smaller{Developed medical image registration algorithms at the Wolfson Medical Vision Laboratory and consulted for Mirada Solutions Ltd.}

### 2024-03-15 papers/composite_inference/notes2024.tex
Update CV

An interesting remark is that the expected ratio $\log p(t_\theta|\theta)/\pi(t_\theta)$ is lower than the true log-likelihood ratio $\log p(x|\theta)/\pi(x)$ by the general fact that the KL~divergence decreases under feature extraction. From there, we can argue that VF likelihood is conservative if used in a Bayesian framework.

>>>>

A key remark is that the expected logarithm ratio $\log p(t_\theta|\theta)/\pi(t_\theta)$ is lower than the true log-likelihood ratio $\log p(x|\theta)/\pi(x)$ by the general fact that the KL~divergence decreases under feature extraction. It is also a direct consequence from the fact that VF likelihood minimizes the KL~divergence among all distributions $p(x)$ compatible with $p(t_\theta|\theta)$.

There is not much we can make from this result alone. But if, by any chance, the reference distribution is chosen so that there exists a $\theta_0$ for which $\pi(x)=p(x|\theta_0)$, then...

(the expectation being taken under the {\em true} unknown distribution)

From there, we can argue that VF likelihood is conservative if used in a Bayesian framework.
